\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-17 Supplymentary.tex
* table 1 updated

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Five Factor Solution {[}Unmerged Responses{]} (24 Items)}
\end{minipage} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}
\end{appendix}

>>>>

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Five Factor Solution {[}Unmerged Responses{]} (24 Items)}
\end{minipage} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}

\hypertarget{geographic-locations-of-survey-participants}{%
\section{Geographic Locations of Survey
Participants}\label{geographic-locations-of-survey-participants}}

\begin{table}

\caption{(\#tab:TzTable)Geographical Location}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{ll}
\toprule
 & N = 690\\
\midrule
Time zone - Country & \\
\hspace{1em}United States - America/New\_York (UTC -04:00) & 63 (9.1\%)\\
\hspace{1em}United Kingdom - Europe/London (UTC) & 57 (8.3\%)\\
\hspace{1em}Germany - Europe/Berlin (UTC +01:00) & 53 (7.7\%)\\
\hspace{1em}India - Asia/Kolkata (UTC +05:30) & 38 (5.5\%)\\
\addlinespace
\hspace{1em}United States - America/Los\_Angeles (UTC -07:00) & 37 (5.4\%)\\
\hspace{1em}United States - America/Chicago (UTC -05:00) & 30 (4.3\%)\\
\hspace{1em}France - Europe/Paris (UTC +01:00) & 22 (3.2\%)\\
\hspace{1em}Switzerland - Europe/Zurich (UTC +01:00) & 21 (3.0\%)\\
\hspace{1em}Brazil - America/Sao\_Paulo (UTC -03:00) & 19 (2.8\%)\\
\addlinespace
\hspace{1em}Netherlands - Europe/Amsterdam (UTC +01:00) & 19 (2.8\%)\\
\hspace{1em}Canada - America/Toronto (UTC -04:00) & 16 (2.3\%)\\
\hspace{1em}Poland - Europe/Warsaw (UTC +01:00) & 15 (2.2\%)\\
\hspace{1em}Canada - America/Edmonton (UTC -06:00) & 14 (2.0\%)\\
\hspace{1em}Finland - Europe/Helsinki (UTC +02:00) & 9 (1.3\%)\\
\addlinespace
\hspace{1em}Indonesia - Asia/Jakarta (UTC +07:00) & 9 (1.3\%)\\
\hspace{1em}Italy - Europe/Rome (UTC +01:00) & 9 (1.3\%)\\
\hspace{1em}Chile - America/Santiago (UTC -03:00) & 8 (1.2\%)\\
\hspace{1em}Russian Federation - Europe/Moscow (UTC +03:00) & 8 (1.2\%)\\
\hspace{1em}China - Asia/Shanghai (UTC +08:00) & 7 (1.0\%)\\
\addlinespace
\hspace{1em}Malaysia - Asia/Kuala\_Lumpur (UTC +08:00) & 7 (1.0\%)\\
\hspace{1em}Spain - Europe/Madrid (UTC +01:00) & 7 (1.0\%)\\
\hspace{1em}United States - America/Phoenix (UTC -07:00) & 7 (1.0\%)\\
\hspace{1em}Canada - America/Vancouver (UTC -07:00) & 6 (0.9\%)\\
\hspace{1em}New Zealand - Pacific/Auckland (UTC +13:00) & 6 (0.9\%)\\
\addlinespace
\hspace{1em}Philippines - Asia/Manila (UTC +08:00) & 6 (0.9\%)\\
\hspace{1em}Turkey - Europe/Istanbul (UTC +03:00) & 6 (0.9\%)\\
\hspace{1em}United States - America/Denver (UTC -06:00) & 6 (0.9\%)\\
\hspace{1em}United States - America/Detroit (UTC -04:00) & 6 (0.9\%)\\
\hspace{1em}Argentina - America/Argentina/Buenos\_Aires (UTC -03:00) & 5 (0.7\%)\\
\addlinespace
\hspace{1em}Australia - Australia/Melbourne (UTC +11:00) & 5 (0.7\%)\\
\hspace{1em}Ireland - Europe/Dublin (UTC) & 5 (0.7\%)\\
\hspace{1em}Lithuania - Europe/Vilnius (UTC +02:00) & 5 (0.7\%)\\
\hspace{1em}South Africa - Africa/Johannesburg (UTC +02:00) & 5 (0.7\%)\\
\hspace{1em}Australia - Australia/Brisbane (UTC +10:00) & 4 (0.6\%)\\
\addlinespace
\hspace{1em}Belgium - Europe/Brussels (UTC +01:00) & 4 (0.6\%)\\
\hspace{1em}Israel - Asia/Jerusalem (UTC +02:00) & 4 (0.6\%)\\
\hspace{1em}Sweden - Europe/Stockholm (UTC +01:00) & 4 (0.6\%)\\
\hspace{1em}United States - America/Boise (UTC -06:00) & 4 (0.6\%)\\
\hspace{1em}Czech Republic - Europe/Prague (UTC +01:00) & 3 (0.4\%)\\
\addlinespace
\hspace{1em}Denmark - Europe/Copenhagen (UTC +01:00) & 3 (0.4\%)\\
\hspace{1em}Germany - Europe/Busingen (UTC +01:00) & 3 (0.4\%)\\
\hspace{1em}Greece - Europe/Athens (UTC +02:00) & 3 (0.4\%)\\
\hspace{1em}Iran & 3 (0.4\%)\\
\hspace{1em}Japan - Asia/Tokyo (UTC +09:00) & 3 (0.4\%)\\
\addlinespace
\hspace{1em}Norway - Europe/Oslo (UTC +01:00) & 3 (0.4\%)\\
\hspace{1em}Romania - Europe/Bucharest (UTC +02:00) & 3 (0.4\%)\\
\hspace{1em}Serbia - Europe/Belgrade (UTC +01:00) & 3 (0.4\%)\\
\hspace{1em}Slovenia - Europe/Ljubljana (UTC +01:00) & 3 (0.4\%)\\
\hspace{1em}Taiwan & 3 (0.4\%)\\
\addlinespace
\hspace{1em}United States - America/Anchorage (UTC -08:00) & 3 (0.4\%)\\
\hspace{1em}United States - America/Indiana/Indianapolis (UTC -04:00) & 3 (0.4\%)\\
\hspace{1em}United States - America/Kentucky/Louisville (UTC -04:00) & 3 (0.4\%)\\
\hspace{1em}Argentina - America/Argentina/Cordoba (UTC -03:00) & 2 (0.3\%)\\
\hspace{1em}Australia - Australia/Adelaide (UTC +10:30) & 2 (0.3\%)\\
\addlinespace
\hspace{1em}Australia - Australia/Perth (UTC +08:00) & 2 (0.3\%)\\
\hspace{1em}Australia - Australia/Sydney (UTC +11:00) & 2 (0.3\%)\\
\hspace{1em}Brazil - America/Araguaina (UTC -03:00) & 2 (0.3\%)\\
\hspace{1em}Brazil - America/Bahia (UTC -03:00) & 2 (0.3\%)\\
\hspace{1em}Canada - America/Moncton (UTC -03:00) & 2 (0.3\%)\\
\addlinespace
\hspace{1em}Colombia - America/Bogota (UTC -05:00) & 2 (0.3\%)\\
\hspace{1em}Costa Rica - America/Costa\_Rica (UTC -06:00) & 2 (0.3\%)\\
\hspace{1em}Croatia - Europe/Zagreb (UTC +01:00) & 2 (0.3\%)\\
\hspace{1em}Ecuador - America/Guayaquil (UTC -05:00) & 2 (0.3\%)\\
\hspace{1em}Estonia - Europe/Tallinn (UTC +02:00) & 2 (0.3\%)\\
\addlinespace
\hspace{1em}Hong Kong - Asia/Hong\_Kong (UTC +08:00) & 2 (0.3\%)\\
\hspace{1em}Hungary - Europe/Budapest (UTC +01:00) & 2 (0.3\%)\\
\hspace{1em}Jordan - Asia/Amman (UTC +03:00) & 2 (0.3\%)\\
\hspace{1em}Latvia - Europe/Riga (UTC +02:00) & 2 (0.3\%)\\
\hspace{1em}Malaysia - Asia/Kuching (UTC +08:00) & 2 (0.3\%)\\
\addlinespace
\hspace{1em}Mexico - America/Mexico\_City (UTC -06:00) & 2 (0.3\%)\\
\hspace{1em}Nepal - Asia/Kathmandu (UTC +05:45) & 2 (0.3\%)\\
\hspace{1em}Portugal - Europe/Lisbon (UTC) & 2 (0.3\%)\\
\hspace{1em}Slovakia - Europe/Bratislava (UTC +01:00) & 2 (0.3\%)\\
\hspace{1em}Spain - Africa/Ceuta (UTC +01:00) & 2 (0.3\%)\\
\addlinespace
\hspace{1em}Sudan - Africa/Khartoum (UTC +02:00) & 2 (0.3\%)\\
\hspace{1em}United States - America/Adak (UTC -09:00) & 2 (0.3\%)\\
\hspace{1em}United States - Pacific/Honolulu (UTC -10:00) & 2 (0.3\%)\\
\hspace{1em}Viet Nam - Asia/Ho\_Chi\_Minh (UTC +07:00),British - America/Tortola (UTC -04:00) & 2 (0.3\%)\\
\hspace{1em}Albania - Europe/Tirane (UTC +01:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Argentina - America/Argentina/Jujuy (UTC -03:00) & 1 (0.1\%)\\
\hspace{1em}Australia - Antarctica/Macquarie (UTC +11:00) & 1 (0.1\%)\\
\hspace{1em}Australia - Australia/Darwin (UTC +09:30) & 1 (0.1\%)\\
\hspace{1em}Austria - Europe/Vienna (UTC +01:00) & 1 (0.1\%)\\
\hspace{1em}Bangladesh - Asia/Dhaka (UTC +06:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Brazil - America/Cuiaba (UTC -04:00) & 1 (0.1\%)\\
\hspace{1em}Brazil - America/Fortaleza (UTC -03:00) & 1 (0.1\%)\\
\hspace{1em}Bulgaria - Europe/Sofia (UTC +02:00) & 1 (0.1\%)\\
\hspace{1em}Cameroon - Africa/Douala (UTC +01:00) & 1 (0.1\%)\\
\hspace{1em}Canada - America/Blanc-Sablon (UTC -04:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Canada - America/Halifax (UTC -03:00) & 1 (0.1\%)\\
\hspace{1em}Canada - America/Resolute (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}Cayman Islands - America/Cayman (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}Chile - Pacific/Easter (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}Cyprus - Asia/Famagusta (UTC +02:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Guatemala - America/Guatemala (UTC -06:00) & 1 (0.1\%)\\
\hspace{1em}Korea,Republic of - Asia/Seoul (UTC +09:00) & 1 (0.1\%)\\
\hspace{1em}Macedonia & 1 (0.1\%)\\
\hspace{1em}Martinique - America/Martinique (UTC -04:00) & 1 (0.1\%)\\
\hspace{1em}Mexico - America/Monterrey (UTC -06:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Mongolia - Asia/Ulaanbaatar (UTC +08:00) & 1 (0.1\%)\\
\hspace{1em}Myanmar - Asia/Yangon (UTC +06:30) & 1 (0.1\%)\\
\hspace{1em}New Zealand - Pacific/Chatham (UTC +13:45) & 1 (0.1\%)\\
\hspace{1em}Nigeria - Africa/Lagos (UTC +01:00) & 1 (0.1\%)\\
\hspace{1em}Pakistan - Asia/Karachi (UTC +05:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Panama - America/Panama (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}Russian Federation - Asia/Barnaul (UTC +07:00) & 1 (0.1\%)\\
\hspace{1em}Russian Federation - Asia/Novosibirsk (UTC +07:00) & 1 (0.1\%)\\
\hspace{1em}Russian Federation - Asia/Tomsk (UTC +07:00) & 1 (0.1\%)\\
\hspace{1em}Russian Federation - Asia/Vladivostok (UTC +10:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Russian Federation - Asia/Yekaterinburg (UTC +05:00) & 1 (0.1\%)\\
\hspace{1em}Saudi Arabia - Asia/Riyadh (UTC +03:00) & 1 (0.1\%)\\
\hspace{1em}Singapore - Asia/Singapore (UTC +08:00) & 1 (0.1\%)\\
\hspace{1em}Spain - Atlantic/Canary (UTC) & 1 (0.1\%)\\
\hspace{1em}Tanzania & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Ukraine - Europe/Kiev (UTC +02:00) & 1 (0.1\%)\\
\hspace{1em}United States - America/Indiana/Tell\_City (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}United States - America/North\_Dakota/Center (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}United States - America/North\_Dakota/New\_Salem (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}Aland Islands - Europe/Mariehamn (UTC +02:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Afghanistan - Asia/Kabul (UTC +04:30) & 0 (0\%)\\
\hspace{1em}Algeria - Africa/Algiers (UTC +01:00) & 0 (0\%)\\
\hspace{1em}American Samoa - Pacific/Pago\_Pago (UTC -11:00) & 0 (0\%)\\
\hspace{1em}Andorra - Europe/Andorra (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Angola - Africa/Luanda (UTC +01:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Anguilla - America/Anguilla (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Casey (UTC +11:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Davis (UTC +07:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/DumontDUrville (UTC +10:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Mawson (UTC +05:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Antarctica - Antarctica/McMurdo (UTC +13:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Palmer (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Rothera (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Syowa (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Troll (UTC) & 0 (0\%)\\
\addlinespace
\hspace{1em}Antarctica - Antarctica/Vostok (UTC +06:00) & 0 (0\%)\\
\hspace{1em}Antigua and Barbuda - America/Antigua (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/Catamarca (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/La\_Rioja (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/Mendoza (UTC -03:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Argentina - America/Argentina/Rio\_Gallegos (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/Salta (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/San\_Juan (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/San\_Luis (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/Tucuman (UTC -03:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Argentina - America/Argentina/Ushuaia (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Armenia - Asia/Yerevan (UTC +04:00) & 0 (0\%)\\
\hspace{1em}Aruba - America/Aruba (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Australia - Australia/Broken\_Hill (UTC +10:30) & 0 (0\%)\\
\hspace{1em}Australia - Australia/Currie (UTC +11:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Australia - Australia/Eucla (UTC +08:45) & 0 (0\%)\\
\hspace{1em}Australia - Australia/Hobart (UTC +11:00) & 0 (0\%)\\
\hspace{1em}Australia - Australia/Lindeman (UTC +10:00) & 0 (0\%)\\
\hspace{1em}Australia - Australia/Lord\_Howe (UTC +11:00) & 0 (0\%)\\
\hspace{1em}Azerbaijan - Asia/Baku (UTC +04:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Bahamas - America/Nassau (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Bahrain - Asia/Bahrain (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Barbados - America/Barbados (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Belarus - Europe/Minsk (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Belize - America/Belize (UTC -06:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Benin - Africa/Porto-Novo (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Bermuda - Atlantic/Bermuda (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Bhutan - Asia/Thimphu (UTC +06:00),Plurinational State of - America/La\_Paz (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Bolivia,Sint Eustatius and Saba - America/Kralendijk (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Bonaire & 0 (0\%)\\
\addlinespace
\hspace{1em}Bosnia and Herzegovina - Europe/Sarajevo (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Botswana - Africa/Gaborone (UTC +02:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Belem (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Boa\_Vista (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Campo\_Grande (UTC -04:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Brazil - America/Eirunepe (UTC -05:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Maceio (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Manaus (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Noronha (UTC -02:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Porto\_Velho (UTC -04:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Brazil - America/Recife (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Rio\_Branco (UTC -05:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Santarem (UTC -03:00) & 0 (0\%)\\
\hspace{1em}British Indian Ocean Territory - Indian/Chagos (UTC +06:00) & 0 (0\%)\\
\hspace{1em}Brunei Darussalam - Asia/Brunei (UTC +08:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Burkina Faso - Africa/Ouagadougou (UTC) & 0 (0\%)\\
\hspace{1em}Burundi - Africa/Bujumbura (UTC +02:00) & 0 (0\%)\\
\hspace{1em}Cambodia - Asia/Phnom\_Penh (UTC +07:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Atikokan (UTC -05:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Cambridge\_Bay (UTC -06:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Canada - America/Creston (UTC -07:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Dawson (UTC -07:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Dawson\_Creek (UTC -07:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Fort\_Nelson (UTC -07:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Glace\_Bay (UTC -03:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Canada - America/Goose\_Bay (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Inuvik (UTC -06:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Iqaluit (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Nipigon (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Pangnirtung (UTC -04:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Canada - America/Rainy\_River (UTC -05:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Rankin\_Inlet (UTC -05:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Regina (UTC -06:00) & 0 (0\%)\\
\hspace{1em}Canada - America/St\_Johns (UTC -02:30) & 0 (0\%)\\
\hspace{1em}Canada - America/Swift\_Current (UTC -06:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Canada - America/Thunder\_Bay (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Whitehorse (UTC -07:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Winnipeg (UTC -05:00) & 0 (0\%)\\
\hspace{1em}Canada - America/Yellowknife (UTC -06:00) & 0 (0\%)\\
\hspace{1em}Cape Verde - Atlantic/Cape\_Verde (UTC -01:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Central African Republic - Africa/Bangui (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Chad - Africa/Ndjamena (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Chile - America/Punta\_Arenas (UTC -03:00) & 0 (0\%)\\
\hspace{1em}China - Asia/Urumqi (UTC +06:00) & 0 (0\%)\\
\hspace{1em}Christmas Island - Indian/Christmas (UTC +07:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Cocos (Keeling) Islands - Indian/Cocos (UTC +06:30) & 0 (0\%)\\
\hspace{1em}Comoros - Indian/Comoro (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Congo - Africa/Brazzaville (UTC +01:00),the Democratic Republic of the - Africa/Kinshasa (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Congo,the Democratic Republic of the - Africa/Lubumbashi (UTC +02:00) & 0 (0\%)\\
\hspace{1em}Congo & 0 (0\%)\\
\addlinespace
\hspace{1em}Cook Islands - Pacific/Rarotonga (UTC -10:00) & 0 (0\%)\\
\hspace{1em}Cuba - America/Havana (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Curaçao - America/Curacao (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Cyprus - Asia/Nicosia (UTC +02:00) & 0 (0\%)\\
\hspace{1em}Côte dIvoire - Africa/Abidjan (UTC) & 0 (0\%)\\
\addlinespace
\hspace{1em}Djibouti - Africa/Djibouti (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Dominica - America/Dominica (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Dominican Republic - America/Santo\_Domingo (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Ecuador - Pacific/Galapagos (UTC -06:00) & 0 (0\%)\\
\hspace{1em}Egypt - Africa/Cairo (UTC +02:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}El Salvador - America/El\_Salvador (UTC -06:00) & 0 (0\%)\\
\hspace{1em}Equatorial Guinea - Africa/Malabo (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Eritrea - Africa/Asmara (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Ethiopia - Africa/Addis\_Ababa (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Falkland Islands (Malvinas) - Atlantic/Stanley (UTC -03:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Faroe Islands - Atlantic/Faroe (UTC) & 0 (0\%)\\
\hspace{1em}Fiji - Pacific/Fiji (UTC +12:00) & 0 (0\%)\\
\hspace{1em}French Guiana - America/Cayenne (UTC -03:00) & 0 (0\%)\\
\hspace{1em}French Polynesia - Pacific/Gambier (UTC -09:00) & 0 (0\%)\\
\hspace{1em}French Polynesia - Pacific/Marquesas (UTC -09:30) & 0 (0\%)\\
\addlinespace
\hspace{1em}French Polynesia - Pacific/Tahiti (UTC -10:00) & 0 (0\%)\\
\hspace{1em}French Southern Territories - Indian/Kerguelen (UTC +05:00) & 0 (0\%)\\
\hspace{1em}Gabon - Africa/Libreville (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Gambia - Africa/Banjul (UTC) & 0 (0\%)\\
\hspace{1em}Georgia - Asia/Tbilisi (UTC +04:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Ghana - Africa/Accra (UTC) & 0 (0\%)\\
\hspace{1em}Gibraltar - Europe/Gibraltar (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Greenland - America/Danmarkshavn (UTC) & 0 (0\%)\\
\hspace{1em}Greenland - America/Nuuk (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Greenland - America/Scoresbysund (UTC -01:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Greenland - America/Thule (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Grenada - America/Grenada (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Guadeloupe - America/Guadeloupe (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Guam - Pacific/Guam (UTC +10:00) & 0 (0\%)\\
\hspace{1em}Guernsey - Europe/Guernsey (UTC) & 0 (0\%)\\
\addlinespace
\hspace{1em}Guinea - Africa/Conakry (UTC) & 0 (0\%)\\
\hspace{1em}Guinea-Bissau - Africa/Bissau (UTC) & 0 (0\%)\\
\hspace{1em}Guyana - America/Guyana (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Haiti - America/Port-au-Prince (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Holy See (Vatican City State) - Europe/Vatican (UTC +01:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Honduras - America/Tegucigalpa (UTC -06:00) & 0 (0\%)\\
\hspace{1em}Iceland - Atlantic/Reykjavik (UTC) & 0 (0\%)\\
\hspace{1em}Indonesia - Asia/Jayapura (UTC +09:00) & 0 (0\%)\\
\hspace{1em}Indonesia - Asia/Makassar (UTC +08:00) & 0 (0\%)\\
\hspace{1em}Indonesia - Asia/Pontianak (UTC +07:00),Islamic Republic of - Asia/Tehran (UTC +03:30) & 0 (0\%)\\
\addlinespace
\hspace{1em}Iraq - Asia/Baghdad (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Isle of Man - Europe/Isle\_of\_Man (UTC) & 0 (0\%)\\
\hspace{1em}Jamaica - America/Jamaica (UTC -05:00) & 0 (0\%)\\
\hspace{1em}Jersey - Europe/Jersey (UTC) & 0 (0\%)\\
\hspace{1em}Kazakhstan - Asia/Almaty (UTC +06:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Kazakhstan - Asia/Aqtau (UTC +05:00) & 0 (0\%)\\
\hspace{1em}Kazakhstan - Asia/Aqtobe (UTC +05:00) & 0 (0\%)\\
\hspace{1em}Kazakhstan - Asia/Atyrau (UTC +05:00) & 0 (0\%)\\
\hspace{1em}Kazakhstan - Asia/Oral (UTC +05:00) & 0 (0\%)\\
\hspace{1em}Kazakhstan - Asia/Qostanay (UTC +06:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Kazakhstan - Asia/Qyzylorda (UTC +05:00) & 0 (0\%)\\
\hspace{1em}Kenya - Africa/Nairobi (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Kiribati - Pacific/Enderbury (UTC +13:00) & 0 (0\%)\\
\hspace{1em}Kiribati - Pacific/Kiritimati (UTC +14:00) & 0 (0\%)\\
\hspace{1em}Kiribati - Pacific/Tarawa (UTC +12:00),Democratic Peoples Republic of - Asia/Pyongyang (UTC +09:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Korea & 0 (0\%)\\
\hspace{1em}Kuwait - Asia/Kuwait (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Kyrgyzstan - Asia/Bishkek (UTC +06:00) & 0 (0\%)\\
\hspace{1em}Lao Peoples Democratic Republic - Asia/Vientiane (UTC +07:00) & 0 (0\%)\\
\hspace{1em}Lebanon - Asia/Beirut (UTC +02:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Lesotho - Africa/Maseru (UTC +02:00) & 0 (0\%)\\
\hspace{1em}Liberia - Africa/Monrovia (UTC) & 0 (0\%)\\
\hspace{1em}Libya - Africa/Tripoli (UTC +02:00) & 0 (0\%)\\
\hspace{1em}Liechtenstein - Europe/Vaduz (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Luxembourg - Europe/Luxembourg (UTC +01:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Macao - Asia/Macau (UTC +08:00),the Former Yugoslav Republic of - Europe/Skopje (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Madagascar - Indian/Antananarivo (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Malawi - Africa/Blantyre (UTC +02:00) & 0 (0\%)\\
\hspace{1em}Maldives - Indian/Maldives (UTC +05:00) & 0 (0\%)\\
\hspace{1em}Mali - Africa/Bamako (UTC) & 0 (0\%)\\
\addlinespace
\hspace{1em}Malta - Europe/Malta (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Marshall Islands - Pacific/Kwajalein (UTC +12:00) & 0 (0\%)\\
\hspace{1em}Marshall Islands - Pacific/Majuro (UTC +12:00) & 0 (0\%)\\
